%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{1pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize} \vspace{-3pt}}
\newcommand{\resumeItemListEnd}{\end{itemize} \vspace{-1pt}}
\renewcommand{\baselinestretch}{1.0}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://nwilcoxnz.co.nz}{\Large Nicole Wilcox}} &  \href{mailto:nwilcoxnz@gmail.com}{nwilcoxnz@gmail.com}\\
 {Software Engineer} & +64-21-205-0941 \\
 &\href{www.nwilcox.co.nz}{nwilcox.co.nz}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Massey University}{Auckland, NZ}
      {Bachelor of Science (Computer Science)}{2012 -- 2015}
  \resumeSubHeadingListEnd
  
  % --------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{\textbf{Languages/Frameworks}{: Javascript, CSS, HTML, React, Typescript, Python, C\#}}
   \item{\textbf{Tools/Technologies/Methodologies}{: Git, Sourcetree, Bash, TFS, IIS, npm, grunt, 
Human Centred Design, OWASP, Agile, SecDevOps}}
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
      \resumeSubheading
      {ASB Bank (HomeShare)}{Auckland, NZ}
      {Tech Lead}{March 2019 - Present}
      \par{Fixed term role; responsibilities include delivering an innovative product to market which addresses the needs of those in shared home ownership.}
      \resumeItemListStart
        \resumeItem{Web app}
          {Assisting in developing and managing the end product, enabling customers to generate a co-ownership contract as well as track their contributions towards their shared home. }
         {\textit{Technologies used:} React, HTML, SCSS, webpack}
        \resumeItem{Automated customer verification tool}
          {Working to create a tool to verify the identity of HomeShare customers, subsequently pulling loan data from ASB to be served through the HomeShare platform.}
			{\textit{Technologies used: }C\# .NET, IIS, SQL, React, Typescript }
          \resumeItem{Customer testing}
          {Leading the customer testing. This involves using HCD principles to run focus groups and surveys.}
      \resumeItemListEnd

    \resumeSubheading
      {ASB Bank}{Auckland, NZ}
      {Software Engineer}{Oct 2017 - March 2019}
      \par{Responsibilities include developing tools to improve security practices throughout the bank.}
      \resumeItemListStart
        \resumeItem{Dashboards}
          {Created web apps to increase the visibility of security practices and aid in the SecDevOps workflow for customer-facing products.}
         {\textit{Technologies used:} React, C\# .NET API, SSMS, IIS}
          \resumeItem{Outlook plugin}
          {Assisted in maintaining a phishing Outlook plugin. The plugin is designed to make it faster and easier 				for all 4000+ staff to report suspected phishing emails.}
			{\textit{Technologies used:} C\#}
          \resumeItem{Incident response}
          {Improved data processing abilities during active incident response, resulting in more efficient threat detection. Contributed to incident response strategies with team.}
			{\textit{Technologies used: } Python}
      \resumeItemListEnd

      \resumeSubheading
      {ASB Bank}{Auckland, NZ}
      {Graduate Engineer}{Feb 2016 - Oct 2017}
      \par{Rotated through various software development projects and business areas.}
      \resumeItemListStart
        \resumeItem{ASB Website}
          {Worked on front-end components to be used in Adobe Experience Manager (AEM). Diagnosed and fixed issues on both the public website and in AEM.}
{\textit{Technologies used:} Adobe Experience Manager, CSS/HTML, JS, gulp, Octopus.}
        \resumeItem{Appointments Project}
          {Investigated and uncovered the root causes of customer appointment booking problems in branches. Developed recommendations and tested one possible solution with customers and staff. Findings were presented to the CEO and Executive Leadership Team.}
          \resumeItem{Innovation Team}
          {Worked on a range of projects aimed at broadening ASBs customer scope past everyday banking needs. This included developing a Kiwisaver chatbot; experimenting with Artificial Intelligence tools; an Xbox Kinect experience for showcasing projects in branches; VR experience including a Clever Kash game and financial visualisation demo; various web apps.}
          \resumeItem{Security Team}
          {Undertook security training, developed an understanding of security practices within the bank, and created tools such as web apps and Outlook plugins which aimed to improve security practices throughout the bank.}
{\textit{Technologies used:} C\#, HTML/CSS/JS}
      \resumeItemListEnd
      
    \resumeSubheading
      {Nyriad}{Waikato, NZ}
      {QA Engineer/Build Manager}{Sep 2015 - Jan 2016}
      \par{Responsibilities included monitoring and creating automated build processes using Jenkins, monitoring Bitbucket environment and creating/implementing standards (including Gitflow). }

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Personal Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Bela}
      {Bela is an affiliate website created by myself that features on-trend items from AliExpress. It is designed to take the hassle out of finding on-trend items on AliExpress. View at \href{https://bela.co.nz}{https://bela.co.nz.}}
    \resumeSubItem{Affiliate site creator}
      {The affiliate site creator is under development by myself and is derived from Bela. It is designed for anyone to be easily able to set up an affiliate site by cloning the source code, personalising the configuration then generating listings using AliExpress product codes. }
  \resumeSubHeadingListEnd
{\textit{Technologies used:} React, Python, CSS/HTML, webpack, npm, Cloudflare, Github Pages, AliExpress API integration, Google Analytics}

%-------------------------------------------
\end{document}
